Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-08 ms/SI.Rmd
Hold table position

```{r phy-sig, results = "as-is"}
phy_sig_results %>%
  mutate(across(c(kval, lambda, k_pval, lambda_pval), ~format(., digits = 2))) %>%
  kbl(booktabs = TRUE) %>%
  kable_styling(latex_options = "striped")
```

@@

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  mutate(across(c(D, prob_random, prob_brownian), ~format(., digits = 2))) %>%
  kbl(booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

@@

lrt_table_data %>%
  select(-model_type) %>%
  kbl(
    col.names = colnames(.) %>% str_replace_all("resp_var", ""),
    booktabs = TRUE) %>%
  pack_rows(index = base::table(lrt_table_data$model_type)) %>%
  kable_styling(latex_options = "striped")
```

>>>>

```{r phy-sig, results = "as-is"}
phy_sig_results %>%
  mutate(across(c(kval, lambda, k_pval, lambda_pval), ~format(., digits = 2))) %>%
  kbl(booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"))
```

@@

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  mutate(across(c(D, prob_random, prob_brownian), ~format(., digits = 2))) %>%
  kbl(booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position"))
```

@@

lrt_table_data %>%
  select(-model_type) %>%
  kbl(
    col.names = colnames(.) %>% str_replace_all("resp_var", ""),
    booktabs = TRUE) %>%
  pack_rows(index = base::table(lrt_table_data$model_type)) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"))
```
